|

### 2020-06-25 paper.Rmd
Update implementation.

XXX some practical considerations, in particular how to estimate unknown $R$, how to map to the display

@@

FIXME For the display function currently I calculate $R$ for each projection as the current maximum radius among all points, so this is not fixed across views. What is the preferred approach here?

>>>>

By default we calculate $R$ as the maximum $p$ dimensional distance from the center of the distribution. However, this is not robust and might lead to large values because of outlying points. XXX alternatives: percentile based radius? user input radius?

@@
